\chapter{Fundamentals} 	% Produces section heading.  Lower-level

Basics such as theory, definitions, relevant theories, related work and state of the art should be included here.

\section{Instruction included in the original FHBgld word processor template}
\subsection{General definitions}
Die in dieser Formatvorlage beispielhaft enthaltenen Überschriften sind auf die im
konkreten Fall tatsächlich passenden Überschriften anzupassen.
In diesem Teil der Arbeit werden die zum eindeutigen Verständnis unbedingt
erforderlichen Grundlagen und Definitionen sowie die Erklärung wichtiger Begriffe
angeführt.
Die Gliederungspunkte müssen möglichst prägnant bezeichnet werden.
\subsection{Related work / state of research}
Auch die neuesten Entwicklungen und Arbeiten auf diesem Gebiet (Stand der
Wissenschaft oder auch state-of-the-art) sind darzulegen, wobei diese je nach Thema
auch in der 1. Gliederungsebene behandelt werden können.

\section{Ordinary text}
% A '%' character causes TeX to ignore all remaining text on the line,
% and is used for comments like this one.

% sections are begun with similar 
% \subsection and \subsubsection commands.

The ends  of words and sentences are marked by spaces. It doesn't matter how many 
spaces    you type; one is as good as 100.  The
end of   a line counts as a space.

One   or more   blank lines denote the  end 
of  a paragraph.  

Since any number of consecutive spaces are treated
like a single one, the formatting of the input
file makes no difference to
\LaTeX,                % The \LaTeX command generates the LaTeX logo.
but it makes a difference to you.  When you use 
\LaTeX \cite{lamport94},  % \cite inserts a reference, which you define at the end of the document
making your input file as easy to read
as possible will be a great help as you write 
your document and when you change it.  This sample 
file shows how you can add comments to your own input 
file.

Because printing is different from typewriting,
there are a number of things that you have to do
differently when preparing an input file than if
you were just typing the document directly.
Quotation marks like
``this'' 
have to be handled specially, as do quotes within
quotes:
``\,`this'            % \, separates the double and single quote.
is what I just 
wrote, not  `that'\,''.  

Dashes come in three sizes: an 
intra-word 
dash, a medium dash for number ranges like 
1--2, 
and a punctuation 
dash---like 
this.

A sentence-ending space should be larger than the
space between words within a sentence.  You
sometimes have to type special commands in
conjunction with punctuation characters to get
this right, as in the following sentence.
Gnats, gnus, etc.\ all  % `\ ' makes an inter-word space.
begin with G\@.         % \@ marks end-of-sentence punctuation.
You should check the spaces after periods when
reading your output to make sure you haven't
forgotten any special cases.  Generating an
ellipsis
\ldots\               % `\ ' is needed after `\ldots' because TeX 
% ignores spaces after command names like \ldots 
% made from \ + letters.
%
% Note how a `%' character causes TeX to ignore 
% the end of the input line, so these blank lines 
% do not start a new paragraph.
%
with the right spacing around the periods requires
a special command.

\LaTeX\ interprets some common characters as
commands, so you must type special commands to
generate them.  These characters include the
following:
\$ \& \% \# \{ and \}.

In printing, text is usually emphasized with an
\emph{italic}  
type style.  

\begin{em}
	A long segment of text can also be emphasized 
	in this way.  Text within such a segment can be 
	given \emph{additional} emphasis.
\end{em}

It is sometimes necessary to prevent \LaTeX\ from
breaking a line where it might otherwise do so.
This may be at a space, as between the ``Mr.''\ and
``Jones'' in
``Mr.~Jones'',        % ~ produces an unbreakable interword space.
or within a word---especially when the word is a
symbol like
\mbox{\emph{itemnum}} 
that makes little sense when hyphenated across
lines.

Footnotes\footnote{This is an example of a footnote.}
pose no problem.

\LaTeX\ is good at typesetting mathematical formulas
like
\( x-3y + z = 7 \) 
or
\( a_{1} > x^{2n} + y^{2n} > x' \)
or  
\( AB  = \sum_{i} a_{i} b_{i} \).
The spaces you type in a formula are 
ignored.  Remember that a letter like
$x$                   % $ ... $  and  \( ... \)  are equivalent
is a formula when it denotes a mathematical
symbol, and it should be typed as one.
Furthermore you can add a formula as Images or Tables, see Formula  \hyperref[eq:abc]{\ref{eq:abc}}
\begin{equation}
	\label{eq:abc}
	a+b=c
\end{equation}

It is sometimes necessary to prevent \LaTeX\ from
breaking a line where it might otherwise do so.
This may be at a space, as between the ``Mr.''\ and
``Jones'' in
``Mr.~Jones'',        % ~ produces an unbreakable interword space.
or within a word---especially when the word is a
symbol like
\mbox{\emph{itemnum}} 
that makes little sense when hyphenated across
lines.