\chapter{Methodology}

Approach, methods, and objectives should come here.

\section{Instruction included in the original FHBgld word processor template}
\subsection{Approach}
Alle im durchgeführten Untersuchungen und Versuche müssen systematisch und
nachvollziehbar sein. Daher ist die gewählte Vorgangsweise genau zu beschreiben
und zu begründen. Es empfiehlt sich, dafür Literatur zum wissenschaftlichen Arbeiten
heranzuziehen.
\subsection{Research methods}
Die eingesetzte Methoden (z.B. Online-Befragung, Inhaltsanalyse, Interviews) müssen
ebenfalls nachvollziehbar beschrieben werden.
Unterschiedliche Untersuchungsmethoden haben oft unterschiedliche Genauigkeit.
Neben der Begründung und Beschreibung der Untersuchungsmethoden ist auch eine
Begründung und Beschreibung der verwendeten Auswertungsmethoden bzw. dafür
verwendete Software unerlässlich\footnote{Wenn der Abstand zwischen Fußnotentrennstrich und Fußnote zu groß wird, gehen Sie folgend vor:
	Wählen Sie im Hauptmenü „Ansicht | Entwurf | Verweise | Notizen anzeigen |
	Fußnotentrennlinie". Dann können Sie unnötige Leerzeichen entfernen.
}.
Wenn es ein Kapitel 3.2.1 gibt, muss es auch ein Kapitel 3.2.2 geben.

\subsubsection{<<Überschrift 4. Ebene>>}
4 Überschriftenebenen müssen reichen.


\section{Displayed Text}
Text is displayed by indenting it from the left
margin.  Quotations are commonly displayed.  There
are short quotations
\begin{quote}
	This is a short quotation.  It consists of a 
	single paragraph of text.  See how it is formatted.
\end{quote}
and longer ones.
\begin{quotation}
	This is a longer quotation.  It consists of two
	paragraphs of text, neither of which are
	particularly interesting.
	
	This is the second paragraph of the quotation.  It
	is just as dull as the first paragraph.
\end{quotation}
Another frequently-displayed structure is a list.
The following is an example of an \emph{itemized}
list.
\begin{itemize}
	\item This is the first item of an itemized list.
	Each item in the list is marked with a ``tick''.
	You don't have to worry about what kind of tick
	mark is used.
	
	\item This is the second item of the list.  It
	contains another list nested inside it.  The inner
	list is an \emph{enumerated} list.
	\begin{enumerate}
		\item This is the first item of an enumerated 
		list that is nested within the itemized list.
		
		\item This is the second item of the inner list.  
		\LaTeX\ allows you to nest lists deeper than 
		you really should.
	\end{enumerate}
	This is the rest of the second item of the outer
	list.  It is no more interesting than any other
	part of the item.
	\item This is the third item of the list.
\end{itemize}
You can even display poetry.
\begin{verse}
	There is an environment 
	for verse \\             % The \\ command separates lines
	Whose features some poets % within a stanza.
	will curse.   
	
	% One or more blank lines separate stanzas.
	
	For instead of making\\
	Them do \emph{all} line breaking, \\
	It allows them to put too many words on a line when they'd rather be 
	forced to be terse.
\end{verse}

Mathematical formulas may also be displayed.  A
displayed formula 
is 
one-line long; multiline
formulas require special formatting instructions.
\[  \Gamma \times  \psi = x'' + y^{2} + z_{i}^{n}\]
Don't start a paragraph with a displayed equation,
nor make one a paragraph by itself.
