\chapter{Synopsis}

\section{Instruction included in the original FHBgld word processor template}
Die Zusammenfassung stellt die gesamte Arbeit – von der Einleitung bis zu den Ergebnissen - in Kurzform dar. Länge maximal 1,5 - 2 Seiten. 

\section{Algorithms}

If you want to show algorithms in your Thesis take a look at the \url{https://www.overleaf.com/learn/latex/algorithms} page. The \verb|algorithm2e| package is already included in the template. You can list algorithms in the same way as you can list Tables and Figures.

\begin{algorithm}[H]
	\KwData{this text}
	\KwResult{how to write algorithm with \LaTeX2e }
	initialization\;
	\While{not at end of this document}{
		read current\;
		\eIf{understand}{
			go to next section\;
			current section becomes this one\;
		}{
			go back to the beginning of current section\;
		}
	}
	\caption{How to write algorithms}
\end{algorithm}
%\cleardoublepage{}

\section{Acronyms and Glossary.}

if you want to use Acronyms or a Glossary check the page here: \url{https://www.overleaf.com/learn/latex/glossaries}

The \Gls{latex} typesetting markup language is specially suitable 
for documents that include \gls{maths}. are 
rendered properly an easily once one gets used to the commands.

Given a set of numbers, there are elementary methods to compute 
its \glsxtrlong{gcd}, which is abbreviated \glsxtrshort{gcd}. This 
process is similar to that used for the \glsxtrfull{lcm}.

\section{Macros}

You can also add useful packages or macros into the \verb|packages_macros.tex| file to add them to the project.
The packages for algorithms, code or the glossary have already been added there.

\subsection{FixMe}
Another example, the \verb|FixMe| package, is added as well. It allows you or your supervisor to add Meta comments to the document. These comments only appear if you set the draft mode in the \verb|main.tex| file. If you remove or comment the activation of the draft mode you can see your final thesis without comments.